Hypertension and microbiome

### 2019-05-20 comparepseqs.Rmd
Minor

#         "data/phfinrisk_16S_otu_raw_2019-02-19.RDs",
     #         "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
     #         "data/phfinrisk_custom70_species_all_2019-01-29.RDs",

@@

```{r rds files}
rds <- list("shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs")
```

>>>>

@@

```{r rds files}
rds <- list("R16S" = "data/phfinrisk_16S_otu_raw_2019-02-19.RDs",
            "shogun" = "data/phfinrisk_species_all_drop50k_2018-12-21.RDs",
            "centrifuge" = "data/phfinrisk_centrifuge_species_all_2018-11-30.RDs",
            "gtdb" = "data/phfinrisk_gtdb_species_all_drop50k_2019-01-14.RDs",
            "ncbi" = "data/phfinrisk_custom70_species_all_2019-01-29.RDs")
```

### 2019-05-20 lactobacillus.Rmd
Minor

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
```

>>>>

```{r libraries}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
```
